---
title: "Data Analysis"
author: "Chelsea Woodruff"
date: "4/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
cleandata <- read.csv("./myData_sub.csv")

install.packages("ggplot2")
install.packages("gridExtra")     
install.packages("scatterplot3d") 
install.packages("MASS") 
library(ggplot2)
library(gridExtra)
library(scatterplot3d)
library(MASS)
```


To analyze the relationship that the demographics may have had with the maximum  price the respondent was willing to pay, we need to create a linear model including all variables:
```{r}

mymodel <- lm(Q2 ~ Education + Gender + Income + Age + HumanInterference + EquityDevelopment + HumansOverNature + DutiesNonhumans, data = cleandata)

summary(mymodel)

```
```{r}
anova(mymodel)
```

Next we might want to see if we can isolate just the demographic varibales to narrow our model's focus:
```{r}
demolm <- lm(Q2 ~ Education + Gender + Income + Age, data = cleandata)
summary(demolm)
```

We'll do the same for the Environmental Attitudes variables:
```{r}
attitudeslm <- lm(Q2 ~ HumanInterference + EquityDevelopment + HumansOverNature + DutiesNonhumans, data = cleandata)
summary(attitudeslm)
```

The AIC stepwise test is to build a predicting model by adding and eliminating variables:
```{r}
mymod2 <- step(mymodel, scope = ~.^2)

summary(mymod2)
```
We must use the last output with the smallest AIC number as our useable result to this test.
With the Adjusted R-squared value of 0.1129, this indicates that 11% of variation is explained through regression line.
```{r}
Agelm <- lm(Q2 ~ Age, data = cleandata)
summary(Agelm)
```

```{r}

boxplot(Q2 ~ Income, xlab = 'Income in Tiers', ylab = 'Price', main = 'Income vs. Price', data = cleandata)

```
```{r}
boxplot(Q2 ~ Education, xlab = 'Education in Tiers', ylab = 'Price', main = 'Education vs. Price', data = cleandata)
```

```{r}
library(stats)
plot(Q2 ~ Age, xlab = 'Age', ylab = 'Price', main = 'Age vs. Price', data = cleandata)
abline(Agelm, col="blue")
```
```{r}
library(stats)
incomelm <- lm(Q2 ~ Income, data = cleandata)
plot(Q2 ~ Income, xlab = 'Income', ylab = 'Price', main = 'Income vs. Price', data = cleandata)
abline(incomelm, col="blue")
```

```{r}
HumanInterferencelm <- lm(Q2 ~ HumanInterference, data = cleandata)
summary(HumanInterferencelm)
```
```{r}
plot(Q2 ~ HumanInterference, xlab = 'Human Interference', ylab = 'Price', main = 'Human Interference vs. Price', data = cleandata)
abline(HumanInterferencelm, col="blue")
```
```{r}
boxplot(Q2 ~ HumanInterference, xlab = 'Human Interference', ylab = 'Price', main = 'Human Interference vs. Price', data = cleandata)
```
```{r}
anova(HumanInterferencelm)
```


We also want to see the results of an anova analysis to examine interaction:
```{r}
anova(mymod2)
```
From above we can see some interaction happening. Most notably with the income and age variables. Human interference is the only solo variable to have a statstically significant P-value. 



