---
title: "Data Analysis"
author: "Chelsea Woodruff"
date: "4/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
cleandata <- read.csv("./myData_sub.csv")

install.packages("ggplot2")
install.packages("gridExtra")     
install.packages("scatterplot3d") 
install.packages("MASS") 
library(ggplot2)
library(gridExtra)
library(scatterplot3d)
library(MASS)
```


To analyze the relationship that the demographics may have had with the maximum  price the respondent was willing to pay, we need to create a linear model including all variables:
```{r}

mymodel <- lm(Q2 ~ Education + Gender + Income + Age + HumanInterference + EquityDevelopment + HumansOverNature + DutiesNonhumans, data = cleandata)

summary(mymodel)

```

The AIC stepwise test is to show __ We will continue with the AIC stepwise analysis:
```{r}
mymod2 <- step(mymodel, scope = ~.^2)

summary(mymod2)
```
We must use the last output with the smallest AIC number as our useable result to this test.
With the Adjusted R-squared value of 0.1129, this indicates that 11% of variation is explained through regression line.
```{r}
Agelm <- lm(Q2 ~ Age, data = cleandata)
```

```{r}

boxplot(Q2 ~ Income, xlab = 'Income in Tiers', ylab = 'Price', main = 'Income vs. Price', data = cleandata)
boxplot(Q2 ~ Education, xlab = 'Education in Tiers', ylab = 'Price', main = 'Education vs. Price', data = cleandata)
plot(Q2 ~ Age, xlab = 'Age', ylab = 'Price', main = 'Age vs. Price', data = cleandata)
albine(Agelm)
```

We also want to see the results of an anova analysis to examine interaction:
```{r}
anova(mymod2)
```
```{r, echo=FALSE}
library(dplyr)
HumIn <- c("Q5", "Q6", "Q7", "Q8", "Q9", "Q10", "Q11", "Q12")
HumIn <- cleandata[HumIn]
CorHumin<- cor(HumIn)
CorPlotHumin <- corrplot(CorHumin, method="circle")
```
