---
title: "Woodruff - Thesis - R code"
author: "Chelsea Woodruff"
date: "3/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
First we must upload the raw data from Qualtrics and clean it up nicely. We skip the first two rows because they include unwanted metadata provided by Qualtrics.
```{r}
myData0305 <- read.csv("./RawDatafromQualtrics.csv")

myData <- read.csv(paste("./RawDatafromQualtrics.csv"), skip=2)

#Next we rename the columns so we can organize the processes better.

names(myData) <- c("StartDate", "EndDate", "IPStatus", "Progress", "DurationSec", "Finished", "RecDate", "ResponseID", "DistChannel", "UserLang", "WouldBuy", "Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Q7", "Q8", "Q9", "Q10", "Q11", "Q12", "Q13", "Q14", "Q15", "Q16", "Q17", "Q18", "Q19", "Q20", "Q21", "Q22", "Q23", "Q24", "Q25", "PriorKnowledge", "Gender", "YearBorn", "ZipCode", "Income", "Race", "Education", "Citizen", "Q34", "Q35", "Q36")

#Next we must change the tiers of education indicated by the respondents to be numerical:

myData$Education <- ifelse(myData$Education =="Less than high school diploma", 1,
  ifelse(myData$Education =="High school degree or equivalent (e.g. GED)", 2,
  ifelse(myData$Education =="Some college, no degree", 3,
  ifelse(myData$Education =="Associate degree (e.g. AA, AS)", 4,
  ifelse(myData$Education =="Bachelor’s degree (e.g. BA, BS)", 5,
  ifelse(myData$Education =="Master’s degree (e.g. MA, MS, MEd)", 6,
  ifelse(myData$Education =="Professional degree (e.g. MD, DDS, DVM)", 7,
  ifelse(myData$Education =="Doctorate (e.g. PhD, EdD)", 8, 'FAIL'
))))))))

#And again for income tiers:

myData$Income <- ifelse(myData$Income =="Less than $10,000", 1,
  ifelse(myData$Income =="$10,000 - $24,999", 2, 
  ifelse(myData$Income =="$25,000 - $49,999", 3, 
  ifelse(myData$Income =="$50,000 - $74,999", 4,
  ifelse(myData$Income =="$75,000 - $99,999", 5,
  ifelse(myData$Income =="$100,000 - $124,999", 6,
  ifelse(myData$Income =="$125,000 - $149,999", 7, 
  ifelse(myData$Income =="$150,000 - $174,999", 8,
  ifelse(myData$Income =="$175,000 – $199,999", 9,
  ifelse(myData$Income =="$200,000 and higher", 10, 'FAIL'
  ))))))))))

#We change the races to 1 or 0 whether the respondent indicated if they were minority or not:

myData$Race <- ifelse(myData$Race == 'White or Caucasian', 1, 0)
```

Because some respondents did not answer all questions, we need to turn missing responses into NA expressions so we can still work with the data without getting error messages.
```{r}
q2price = gsub("$", "", as.character(myData$Q2), fixed=T)
tmp = unlist(lapply(strsplit(q2price, ","), function(x) max(as.numeric(x))))
tmp = ifelse(is.infinite(tmp), NA, tmp)
myData$Q2 = tmp
myData_sub = na.omit(myData)
```

Next we need to write code to change the Likert-scale answers between Strongly Agree to Strongly Disagree into numerical values. Eventually we will use these values to find the average of the groups of questions. For example: Questions 5-12 ask the respondent how strongly they feel about statements regarding human interference with nature. So we titled Questions 5-12 Human Interference. 

Environmental and Social Views Categories: HI (Human Interference), ED (Equity and Development), HON (Humans Over Nature), NON (Duties to Nonhumans)

These are the statements asked of the respondents:
Q5: HI: Present levels of industrial activity are severely upsetting the natural environment.
Q6: HI: Present levels of industrial activity are excessive and need to be reduced.
Q7: HI: Humans should adapt to nature rather than modify it to suit us.
Q8: HI: A change in basic attitudes is necessary in order to solve environmental problems.
Q9: HI: Humans should live in harmony with the rest of nature.
Q10: HI: Human interference with nature often results in disastrous consequences.
Q11: HI: Humans are presently interfering too much with the natural environment.
Q12: HI: People should have compassion and respect for the rest of nature.

Q13: ED: There are limits to industrial growth.
Q14: ED: Natural resources should be used primarily to provide for basic needs rather than material wealth.
Q15: ED: Humans have moral duties and obligations to other humans.
Q16: ED: Present generations of humans have moral duties and obligations to future human generations.
Q17: ED: Satisfaction and a high quality of life are more important than money or material wealth.

Q18: HON: Reversed: Humans have the right to alter nature to satisfy wants and desire.
Q19: HON: Reversed: Maintaining economic growth is more important than protecting the natural environment.
Q20: HON: Reversed: Humans have the right to reduce the number of species on Earth in order to promote economic development.
Q21: HON: Reversed: Humans have the right to subdue and control the rest of nature.

Q22: NON: The natural environment has value within itself regardles of any value that humans may place on it.
Q23: NON: Humans have moral duties and obligations to other animal species.
Q24: NON: Humans have moral duties and obligations to plants and trees.
Q25: NON: Humans have moral duties and obligations to the non-living components of nature (e.g., rocks).

Some social views need to be reversed because strongly disagree for those are pro-environment. These questions are Questions 18-21. 

```{r}
code_resp <- function(code) {
  code_key = data.frame(code = c('Strongly agree', 'Agree', 'Somewhat agree', 'Neither agree nor disagree', 'Somewhat disagree', 'Disagree', 'Strongly disagree'), 
                                      value = 7:1)
  code_value = code_key$value[match(code, code_key$code)]
  return(code_value)}

myData_sub$Q5<-code_resp(myData_sub$Q5)
myData_sub$Q6<-code_resp(myData_sub$Q6)
myData_sub$Q7<-code_resp(myData_sub$Q7)
myData_sub$Q8<-code_resp(myData_sub$Q8)
myData_sub$Q9<-code_resp(myData_sub$Q9)
myData_sub$Q10<-code_resp(myData_sub$Q10)
myData_sub$Q11<-code_resp(myData_sub$Q11)
myData_sub$Q12<-code_resp(myData_sub$Q12)
myData_sub$Q13<-code_resp(myData_sub$Q13)
myData_sub$Q14<-code_resp(myData_sub$Q14)
myData_sub$Q15<-code_resp(myData_sub$Q15)
myData_sub$Q16<-code_resp(myData_sub$Q16)
myData_sub$Q17<-code_resp(myData_sub$Q17)
myData_sub$Q22<-code_resp(myData_sub$Q22)
myData_sub$Q23<-code_resp(myData_sub$Q23)
myData_sub$Q24<-code_resp(myData_sub$Q24)
myData_sub$Q25<-code_resp(myData_sub$Q25)

code_resp_reverse <- function(code) {
  code_key_reverse = data.frame(code = c('Strongly agree', 'Agree', 'Somewhat agree', 'Neither agree nor disagree', 'Somewhat disagree', 'Disagree', 'Strongly disagree'), 
                                      value = 1:7)
  code_value_reverse = code_key_reverse$value[match(code, code_key_reverse$code)]
  return(code_value_reverse)}

#Questions 18-21 indicated that pro-environment was on the low end of numbers so we must reverse the answers here to still gain accurate averages. These are the reversed answers here:

myData_sub$Q18<-code_resp_reverse(myData_sub$Q18)
myData_sub$Q19<-code_resp_reverse(myData_sub$Q19)
myData_sub$Q20<-code_resp_reverse(myData_sub$Q20)
myData_sub$Q21<-code_resp_reverse(myData_sub$Q21)

# Now we can find the averages of these categories:

myData_sub$HumanInterference <- ((myData_sub$Q5 + myData_sub$Q6 + myData_sub$Q7 + myData_sub$Q8 + myData_sub$Q9 + myData_sub$Q10 + myData_sub$Q11 + myData_sub$Q12)/8)

myData_sub$EquityDevelopment <- ((myData_sub$Q13 + myData_sub$Q14 + myData_sub$Q15 + myData_sub$Q16 + myData_sub$Q17)/5)

myData_sub$HumansOverNature <- ((myData_sub$Q18 + myData_sub$Q19 + myData_sub$Q20 + myData_sub$Q21)/4)

myData_sub$DutiesNonhumans <- ((myData_sub$Q22 + myData_sub$Q23 + myData_sub$Q24 + myData_sub$Q25)/4)

myData_sub$AllViews <- ((myData_sub$Q5 + myData_sub$Q6 + myData_sub$Q7 + myData_sub$Q8 + myData_sub$Q9 + myData_sub$Q10 + myData_sub$Q11 + myData_sub$Q12 + myData_sub$Q13 + myData_sub$Q14 + myData_sub$Q15 + myData_sub$Q16 + myData_sub$Q17 + myData_sub$Q18 + myData_sub$Q19 + myData_sub$Q20 + myData_sub$Q21 + myData_sub$Q22 + myData_sub$Q23 + myData_sub$Q24 + myData_sub$Q25)/21)

# Since we asked what year they were born, we need to change that into the continuous varibale that is age:
```
```{r}
myData_sub$Age <- as.numeric(myData_sub$YearBorn)
myData_sub$Age <- (2019 - myData_sub$YearBorn)
```

Upon further inspection after trying to work with the data, we need to now change the Income and Education tiers into LOW, MODERATE, and HIGH categories to work with easier.
```{r}
myData_sub$Income <- ifelse(myData_sub$Income =="1", "LOW",
ifelse(myData_sub$Income =="2", "LOW", 
ifelse(myData_sub$Income =="3", "LOW", 
ifelse(myData_sub$Income =="4", "MODERATE",
ifelse(myData_sub$Income =="5", "MODERATE",
ifelse(myData_sub$Income =="6", "MODERATE",
ifelse(myData_sub$Income =="7", "MODERATE", 
ifelse(myData_sub$Income =="8", "HIGH",
ifelse(myData_sub$Income =="9", "HIGH",
ifelse(myData_sub$Income =="10", "HIGH", 'FAIL'
))))))))))

myData_sub$Education <- ifelse(myData_sub$Education =="1", "LOW",
ifelse(myData_sub$Education =="2", "LOW", 
ifelse(myData_sub$Education =="3", "LOW", 
ifelse(myData_sub$Education =="4", "MODERATE",
ifelse(myData_sub$Education =="5", "MODERATE",
ifelse(myData_sub$Education =="6", "HIGH",
ifelse(myData_sub$Education =="7", "HIGH", 
ifelse(myData_sub$Education =="8", "HIGH", 'FAIL'
))))))))
```

We need to save all this transformed data separately from the raw data. We will call it myData_sub
```{r}
myData_sub <- write.csv(myData_sub, file = "./myData_sub.csv")
```

